---
title: "MATH4753nguy0398-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH4753nguy0398-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753nguy0398)
```

# Introduction

This package (MATH4753nguy0398) involves the "CODING" dataset, as well as the
functions "_mysample()_", "_mycltmean()_", "_myncurve()_", and "_mymaxlik()_".

## Data

_"coding" Data Set_

A data set containing instances of days elapsed and the number of program 
modules with errors, from 25 randomly-selected program modules

```{r}
data("coding")

knitr::kable(head(coding))

```

## First Function

_"mysample" function_

Generates a given amount of iterations for a given amount of random samples
between 1 and 10 (inclusive) with replacement. Then, graphs the data
to a barplot, before waiting to start the next iteration.

```{r}

MATH4753nguy0398::mysample(n = 10000, iter = 4, time = 0.5)

```

## Second Function

_"mycltmean" function_

Generates an n-sized random sample from the uniform distribution (between 0 
and 5) for a given amount of iterations. Then, calculates the mean value for 
each simulated iterations to form a histogram of this data.

```{r}
MATH4753nguy0398::mycltMean(n = 100, iter = 25)
```

## Third Function

_"myncurve" function_

Displays a normal curve (given mu and sigma), shades in the area between
the curve and the x-axis from -Inf (approximated to 3 SD's away from the mean)
to x=a (given a), and returns the area as a form of probability.

```{r}
MATH4753nguy0398::myncurve(mu = 0, sigma = 1, a = 2)
```

## Fourth Function

_"mymaxlik" function_

Given data, a probability-based function, and a range of potential values,
this function determines the potential value that has the highest likelihood
of generating this data.

```{r}
# size is 20 to account for 20 trials 
logbin=function(x,param) log(dbinom(x,prob=param,size=20))

# each value within results represents the outcome of 1 trial (out of 8)
# in this case, the outcomes for this example is [1,2,3,4,5,6,7,8] successes
# out of the 20 trials
results = c(1,2,3,4,5,6,7,8)

MATH4753nguy0398::mymaxlik(x=results,param=seq(0,1,length=1000),lfun=logbin,xlab=expression(pi),
         main="Binomial",cex.main=2)
```
